\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-17 main.Rmd
rewrote scatterplot

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
read_chunk('src/main.R')
```

@@

## Interactivity

@@

Figure \ref{fig:dow} shows the energy use across days of week in the form of letter value plots [@hofmann2017letter]. As a variant of boxplots, letter value plots represent each pair of adjacent letter values using one box, instead of whiskers. Figure \ref{fig:dow} demonstrates three letter values and outliers marked as asterisks, with a line representing the median (thus M) and the innermost boxes corresponding to the fourth (F) and the eighth quantiles (E). Household 3, with a family size of one couple and two kids, uses more energy over the weekdays given the medians, compared to the others consisting of one or two people. Whereas, household 2 displays a great deal of variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy on average with increased variations during the weekends relative to the weekdays, as a reflection of work and leisure pattern.

@@

A snapshot is taken at a different time resolution to picture individual's energy usage against time of day, across workdays and non-work days. Figure \ref{fig:hod} gives a more detailed depiction of each household's life style. Household 1 appears an early bird, starting the day before 6 and going back home around 18 on workdays. There is an uncommon pattern occurring to household 2 only, with a cluster of points concentrated above 1 kWh across all time of day. It perhaps alerts household 2 to potential electricity leakage. Household 3 shows persistent trimodel behaviors across workdays and non-workdays. Nevertheless, the non-work life of household 4 distinguishes from the workdays when most energy is consumed after 18.

```{r hod, fig.height = 6, fig.cap = "Scatterplot between time of day and half-hourly energy usage, constrasting workdays and non-work days for each household. A distinctive pattern exclusive to household 2 is popped out: a fair amount of points are clustered above 1 kWh over all time of day. (too generic, when they get up and different between work day and non-work days)"}
```

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = FALSE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
read_chunk('src/main.R')
```

@@

### Interactivity

@@

Figure \ref{fig:dow} shows the energy use across days of week in the form of letter value plots [@hofmann2017letter]. As a variant of boxplots, letter value plots represent each pair of adjacent letter values using one box, instead of whiskers. Figure \ref{fig:dow} demonstrates three letter values and outliers marked as asterisks, with a line representing the median (thus M) and the innermost boxes corresponding to the fourth (F) and the eighth quantiles (E). Household 3, with a family size of one couple and two kids, uses more energy over the weekdays given the medians, compared to the others consisting of one or two people. Whereas, household 2 displays a great deal of variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy on average with increased variations during the weekends relative to the weekdays, as a reflection of work and leisure patterns.

@@

Figure \ref{fig:hod} provides a more detailed depiction of each household's life style, by plotting energy consumption against time of day between weekdays and weekends. Household 1 is an early bird, starting their day before 6 and going back home around 18 on weekdays. They switch air conditioning or heating on when they get home from work and keep it operated till mid-night, while learned from the tiny cluster of points below 1 kWh. On the other hand, the strips above 1 kWh tells that household 2 perhaps have air conditioning or heating on all time during the days, consuming the energy almost as double as household 1. Apart from the morning and night peak use, a third peak occurs around 3pm for household 3 only, when the kids are home from school. They also share a consistent energy pattern between weekdays and weekends. As for household 4, their home routine starts after 6pm on weekdays.

```{r hod, fig.height = 6, fig.cap = "Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting weekdays and weekends for each household. All have different daily routines between weekdays and weekends, except for household 3. On weekdays, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2."}
```

### 2018-10-17 main.tex
rewrote scatterplot

\hypertarget{interactivity}{%
\subsection{Interactivity}\label{interactivity}}

@@

Figure \ref{fig:dow} shows the energy use across days of week in the
form of letter value plots \citep{hofmann2017letter}. As a variant of
boxplots, letter value plots represent each pair of adjacent letter
values using one box, instead of whiskers. Figure \ref{fig:dow}
demonstrates three letter values and outliers marked as asterisks, with
a line representing the median (thus M) and the innermost boxes
corresponding to the fourth (F) and the eighth quantiles (E). Household
3, with a family size of one couple and two kids, uses more energy over
the weekdays given the medians, compared to the others consisting of one
or two people. Whereas, household 2 displays a great deal of variability
in daily energy consumption with noticeable variations on Thursdays, and
much higher usage over the weekends. The other two households (1 and 4)
tend to consume more energy on average with increased variations during
the weekends relative to the weekdays, as a reflection of work and
leisure pattern.

@@

A snapshot is taken at a different time resolution to picture
individual's energy usage against time of day, across workdays and
non-work days. Figure \ref{fig:hod} gives a more detailed depiction of
each household's life style. Household 1 appears an early bird, starting
the day before 6 and going back home around 18 on workdays. There is an
uncommon pattern occurring to household 2 only, with a cluster of points
concentrated above 1 kWh across all time of day. It perhaps alerts
household 2 to potential electricity leakage. Household 3 shows
persistent trimodel behaviors across workdays and non-workdays.
Nevertheless, the non-work life of household 4 distinguishes from the
workdays when most energy is consumed after 18.

@@

\caption{Scatterplot between time of day and half-hourly energy usage, constrasting workdays and non-work days for each household. A distinctive pattern exclusive to household 2 is popped out: a fair amount of points are clustered above 1 kWh over all time of day. (too generic, when they get up and different between work day and non-work days)}\label{fig:hod}
\end{figure}

>>>>

\hypertarget{interactivity}{%
\subsubsection{Interactivity}\label{interactivity}}

@@

Figure \ref{fig:dow} shows the energy use across days of week in the
form of letter value plots \citep{hofmann2017letter}. As a variant of
boxplots, letter value plots represent each pair of adjacent letter
values using one box, instead of whiskers. Figure \ref{fig:dow}
demonstrates three letter values and outliers marked as asterisks, with
a line representing the median (thus M) and the innermost boxes
corresponding to the fourth (F) and the eighth quantiles (E). Household
3, with a family size of one couple and two kids, uses more energy over
the weekdays given the medians, compared to the others consisting of one
or two people. Whereas, household 2 displays a great deal of variability
in daily energy consumption with noticeable variations on Thursdays, and
much higher usage over the weekends. The other two households (1 and 4)
tend to consume more energy on average with increased variations during
the weekends relative to the weekdays, as a reflection of work and
leisure routines.

@@

Figure \ref{fig:hod} provides a more detailed depiction of each
household's life style, by plotting energy consumption against time of
day between weekdays and weekends. Household 1 is an early bird,
starting their day before 6 and going back home around 18 on weekdays.
They switch air conditioning or heating on when they get home from work
and keep it operated till mid-night, while learned from the tiny cluster
of points below 1 kWh. On the other hand, the strips above 1 kWh tells
that household 2 perhaps have air conditioning or heating on all time
during the days, consuming the energy almost as double as household 1.
Apart from the morning and night peak use, a third peak occurs around
3pm for household 3 only, when the kids are home from school. They also
share a consistent energy pattern between weekdays and weekends. As for
household 4, their home routine starts after 6pm on weekdays.

@@

\caption{Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting weekdays and weekends for each household. All have different daily routines between weekdays and weekends, except for household 3. On weekdays, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2.}\label{fig:hod}
\end{figure}
